Usenet Project - CSV Cleaning

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
made changes, testing connection

## Loading Libraries
```{r}
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
```
## Read and Clean CSVs
```{r}
# Load necessary libraries
library(dplyr)

# Load Directories
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"

@@

# Display the updated dataframes (optional)
head(all_threads)
head(all_comments)
```
## Fix Date and Time Columns
```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# Function to clean the datetime strings
clean_datetime <- function(dt_str) {
  gsub("[^[:alnum:] [:punct:]]", "", dt_str)
}

@@

# Descriptive Statistics

## Primary
```{r}
# Load necessary library
library(dplyr)
library(sjPlot)

# Print the summary data frame with totals
tab_df(summary_df, file = "Images and Tables/descriptive_statistics_table.html")
```

```{r}
library(knitr)
library(kableExtra)

# Create the table
summary_table <- kable(summary_df, format = "html", table.attr = "style='width:100%;'") %>%
  kable_styling(full_width = FALSE) %>%
  row_spec(0, bold = TRUE) %>%  # Make the first row bold
  row_spec(nrow(summary_df), hline_after = TRUE)  # Add a line after the second to last row

# Print the table
summary_table
```

## Keyword Search Statistics
```{r}
# Load necessary library
library(dplyr)

@@

## Save Keyword CSVs to File
```{r}
# Collect all related threads and comments
related_threads <- all_threads %>%
  filter(Unique_ThreadID %in% threads_with_keywords) %>%
  filter(Date <= as.Date("1988-12-31"))

@@

>>>>

## Loading Libraries
```{r}
library(tidyverse)
library(readr)
library(webshot)
library(htmltools)
# Load necessary library
library(dplyr)
# Load necessary libraries
library(ggplot2)
library(dplyr)
```
## Read and Clean CSVs
```{r}
# Load Directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

@@

# Display the updated dataframes (optional)
head(all_threads)
head(all_comments)
```
## Fix Date and Time Columns
```{r}
# Function to clean the datetime strings
clean_datetime <- function(dt_str) {
  gsub("[^[:alnum:] [:punct:]]", "", dt_str)
}

@@

# Filter Additionally by Keyword
```{r Filter by Keyword}

@@

```{r Save Keyword CSVs to File}
# Collect all related threads and comments
related_threads <- all_threads %>%
  filter(Unique_ThreadID %in% threads_with_keywords) %>%
  filter(Date <= as.Date("1988-12-31"))

@@

# Table and Figures
```{r Descriptive Statistics}
# Load necessary library
library(dplyr)
library(sjPlot)

# Print the summary data frame with totals
tab_df(summary_df, file = paste0(output_directory, "Images and Tables/descriptive_statistics_table.html"))
```
